%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Noah Lee's Professional CV
%
% Original template from:
% https://www.LaTeXTemplates.com
%
% Author:
% Noah Lee (noahlee0514@gmail.com)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

% \usepackage{ebgaramond} % Use the EB Garamond font - Commented out
\usepackage{lato} % Using Lato font
% \usepackage{times} % Example: Times (serif) - Commented out

%------------------------------------------------

\name{Noah Lee} % Your name to appear at the top

% Redefine address separator
\renewcommand{\addressSep}{~|~}

\address{noahlee0514@gmail.com \addressSep 954-501-1598 \addressSep linkedin.com/in/noahilee/}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}

Design Engineer with a background in Computer Engineering, specializing in embedded systems development, firmware, and full-stack application design. Proven ability to develop and implement robust solutions for industrial automation using C, Rust, and Dart/Flutter.

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	\textbf{Rose-Hulman Institute of Technology} \hfill \textit{Terre Haute, IN} \\ 
	Bachelor of Science in Computer Engineering \hfill Graduated: May 2024 \\
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}

    \begin{rSubsection}{FACTS Engineering LLC}{July 2024 -- Present}{Design Engineer}{New Port Richey, FL}
		\item Led full-cycle development of I/O modules for use in industry (schematics, UL compliance, part selection) and firmware (C, industrial protocols), including product lifecycle management (redesigns, value engineering).
		\item \textbf{Unreleased IoT Device Firmware} (November 2024 -- Present): Developed FreeRTOS-based firmware in C for a remote Modbus TCP I/O slave, architecting the network stack and a modular I/O module sign-on sequence.
		\item \textbf{IoT Device Configuration App} (November 2024 -- Present): Designed and developed a cross-platform Flutter application for configuration and real-time monitoring of the I/O slave, utilizing UDP multicasting and TCP communication.
        \item \textbf{Rust-based PLC Driver for RP2350} (September 2024 -- November 2024): Ported our open-source Arduino PLC driver to the Raspberry Pi RP2350 microcontroller, re-implementing core logic in Rust utilizing the Embassy (async) framework for enhanced performance and safety.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Milwaukee Tools}{June 2023 -- August 2023}{Firmware Engineering Intern}{Brookfield, WI}
		\item Developed code in C and C++ to modernize firmware with new features for use in new hardware.
		\item Created and executed a detailed test plan to validate feasibility and implementation of new features.
	\end{rSubsection}
    
\end{rSection}

%----------------------------------------------------------------------------------------
%	PERSONAL PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Personal Projects}

	\begin{rSubsection}{``AudSpec Pico''}{Summer 2022 -- Winter 2022}{Multicore Audio Spectrometer on RP2040 Board}{}
		\item Written in Arduino/C++ for Raspberry Pi Pico board; interfaces with peripherals such as 3.5mm audio, I2C display, and ADC GPIO for FFT calculations to display audio data by frequency.
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Languages & C, Rust, Python (Scripting), Java, Dart (Flutter) \\
        RTOS & FreeRTOS, Rust Embassy \\
		Hardware & Verilog HDL, MCU (STM32, RP2350), FPGA, Picoscope, Hardware Debugging \\
        Protocols \& APIs & Modbus TCP, TCP/IP, UDP, I2C, (REST - if still relevant) \\
		Tools & Git, VS Code, Pads Logic, Altium, IAR, Vivado, Android Studio
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}